Capstone Movielens Report

### 2025-09-24 reports/capstone-movielens.site/02-0.methods.Rmd
Fix fro Section 2.2 Preparing train and set datasets.

We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_. 
To prepare datasets for processing, we will use the following functions, specifically designed for these operations:

@@

We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$. To create this matrix, we use `tidyr::pivot_wider` function:

>>>>

We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_[@IDS2_29-6]. 
To prepare datasets for processing, we will use the following functions, specifically designed for these operations:

@@

We will use the array representation described in [Section 17.5 Analysis of variance (ANOVA)](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook_[@IDS2_17-5], for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$. To create this matrix, we use `tidyr::pivot_wider` function:
